---
title: "Assignment 1 - Data Analytics"
author: "Dyon Pacheco"
date: "1/4/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}

library(quantmod)
library(tidyquant)
library(tidyverse)
library(rvest)

```


Question 1: How did the stock price perform in the last year (Jan 1st 2021 up until today)?
- Include a graph (self-explanatory) 
- Use the quantmode package (yahoo example) 
- Dynamic code (results change when ticker or time input changes) 

```{r}
# Set tickers
ticker1 <- "AAPL"

# Set start and end date
start_date <- as.Date("2021-01-01")
end_date <- as.Date(Sys.Date())

# Get data from Yahoo
stocks_ticker1 <- tq_get(ticker1, get = "stock.prices", from = start_date,to = end_date)


# Plot percent change 
ggplot() + 
  geom_line(data = stocks_ticker1, aes(date, adjusted, color = symbol), size = 1) + 
  scale_color_manual(name = "Ticker",  values = "black") +
  xlab('Dates') +   ylab('Stock Price') +    ggtitle('Stock Price') 


```


Question 2: What would be a relevant benchmark firm? 
- Explain briefly in a few sentences
- Static answer (does not change when ticker or time input changes)

A relevant benchmark firm could be microsoft. beacsue both of them are big tech. They both sell software and hardware (however the mix is different). In my opinion it would be better to benchmark against a group of stocks rather than simply just one stock.

```{r}
# Get data from Yahoo
stocks_ticker2 <- tq_get("MSFT", get = "stock.prices", from = "2021-01-01",to = Sys.Date())


# Plot percent change 
ggplot() + 
  geom_line(data = stocks_ticker2, aes(date, adjusted, color = symbol), size = 1) + 
  scale_color_manual(name = "Ticker",  values = "green") +
  xlab('Dates') +   ylab('Stock Price') +    ggtitle('Stock Price') 


```

Question 3: How did the stock price develop compare to the benchmark in relative terms 
(percent change from Jan 1st 2021). 
- Include a graph (self-explanatory) 
- Dynamic code

```{r}
ggplot() + 
  geom_line(data = stocks_ticker1, aes(date, adjusted, color = symbol), size = 1) + 
  geom_line(data = stocks_ticker2, aes(date, adjusted, color = symbol), size = 1) + 
  scale_color_manual(name = "Ticker",  values = c("black", "green")) +
  xlab('Dates') +   ylab('Stock Price') +    ggtitle('Stock Price') 

#couldnt figure out how to add a percentage rank??

```

Question 4: When was the last earnings announcement? 
- Scrape from Yahoo Finance and get the latest earnings announcement
- Use RVest
- Dynamic code (changes when ticker or time changes (latest)) 
- This is a bit more difficult! 

```{r}
#define the ticker
ticker12 <-"AAPL"

# 1 Define the URL 
read_url <- paste0("https://finance.yahoo.com/calendar/earnings?symbol=",ticker12) 

# 2 Read the html side
publications <- read_html(read_url) %>% 
  # 3 Define the Node
  html_nodes("span") %>%
  # 4 Extract the text from the node
  html_text() %>% 
  data.frame()


#apply regex to fiter out dates into a tibble

publications <- tibble(publications) #coercing df into a tibble

announcement_dates <- publications[28:324,] #segrigating only dates

#need to figue out how to filter out the right date?



```

Question 5: How did the stock price react around the last earnings announcement? 
- Include a graph with the days around the earnings announcement (dynamic)
- Interpret briefly in a few sentences (static)

```{r}


earningsdate <- as.Date("2021-10-28") #changing this date automatically plots the graph we want

estwindow <- tibble() #creating a blank tibble to be read into

estwindow <- filter(stocks_ticker1, date == earningsdate-1) #3 days around the announcement date that we are interested in 
estwindow <- bind_rows(estwindow,filter(stocks_ticker1, date == earningsdate))
estwindow <- bind_rows(estwindow,filter(stocks_ticker1, date == earningsdate+1))

ggplot() + 
  geom_line(data = estwindow, aes(date, adjusted, color = symbol), size = 1) + 
  scale_color_manual(name = "Ticker",  values ="black") +
  xlab('Dates') +   ylab('Stock Price') +    ggtitle('stock price 3 days surrounding earnings announcement') 



```



Question 6: Interpret your overall findings. Is your firm a good investment? 
- Briefly in a few sentences (static)
ggplot() + 
  geom_line(data = stocks_ticker1, aes(date, adjusted, color = symbol), size = 1) + 
  geom_line(data = stocks_ticker2, aes(date, adjusted, color = symbol), size = 1) + 
  scale_color_manual(name = "Ticker",  values = c("black", "green")) +
  xlab('Dates') +   ylab('Stock Price') +    ggtitle('Stock Price') 
yes obiously lol the stock price went to the moon [insert 3 rockt emojis here :P ]

